---
title: "Mobile Phones"
output: flexdashboard::flex_dashboard
runtime: shiny
---


```{r setup, include=FALSE}
library(flexdashboard)
library(shiny)
library(formulaic)
library(rmarkdown)
library(knitr)
#install.packages("Hmisc")
#library(Hmisc)
library(DT)

library(data.table)
assignInNamespace(x = "cedta.override", value = c(data.table:::cedta.override,"rmarkdown"), ns = "data.table")

opts_chunk$set(echo = FALSE, comment="", warning = FALSE, message = FALSE, tidy.opts=list(width.cutoff=55), tidy = TRUE)

```

```{r source_functions}
#source("constants.R")
#source("functions.R")
```

```{r functions}
engagement.model <- function(dt, outcome.name, input.names, model.type){
  res <- fit.model(dt = dt, outcome.name = outcome.name, input.names = input.names, model.type = model.type)
  return(res)
}

fit.model <- function(dt, outcome.name, input.names, model.type, digits = 3){
  library(formulaic)
  the.formula <- create.formula(outcome.name = outcome.name, input.names = input.names, dat = dt, reduce = T)
  
  if(model.type == "logistic"){
    mod <- glm(formula = the.formula, family = "binomial", data = dt)
    mod.summary <- logistic.regression.summary(glm.mod = mod, digits = digits)
  }
  if(model.type == "linear"){
    mod <- lm(formula = the.formula, data = dt)
    mod.summary <- linear.regression.summary(lm.mod = mod, digits = digits)
  }
  mod.summary.rounded <- mod.summary[, lapply(X = .SD, FUN = "round.numerics", digits = digits)]
  return(mod.summary.rounded)
}

logistic.regression.summary <- function(glm.mod, digits = 3, alpha = 0.05){
  library(data.table)
  glm.coefs <- as.data.table(summary(glm.mod)$coefficients, keep.rownames = TRUE)
  setnames(x = glm.coefs, old = "rn", new = "Variable")
  z <- qnorm(p = 1-alpha/2, mean = 0, sd = 1)
  glm.coefs[, Odds.Ratio := exp(Estimate)]
  glm.coefs[, OR.Lower.95 := exp(Estimate - z * `Std. Error`)]
  glm.coefs[, OR.Upper.95 := exp(Estimate + z * `Std. Error`)]
  
  return(glm.coefs[])
}



linear.regression.summary <- function(lm.mod, digits = 3, alpha = 0.05){
  library(data.table)
  lm.coefs <- as.data.table(summary(lm.mod)$coefficients, keep.rownames = TRUE)
  setnames(x = lm.coefs, old = "rn", new = "Variable")

  z <- qnorm(p = 1-alpha/2, mean = 0, sd = 1)
  lm.coefs[, Coef.Lower.95 := Estimate - z * `Std. Error`]
  lm.coefs[, Coef.Upper.95 := Estimate + z * `Std. Error`]
  return(lm.coefs)
}

percentage.table <- function(x, digits = 1){
  tab <- table(x)
  percentage.tab <- 100*tab/(sum(tab))
  rounded.tab <- round(x = percentage.tab, digits = digits)
  return(rounded.tab)
}

round.numerics <- function(x, digits){
  if(is.numeric(x)){
    x <- round(x = x, digits = digits)
  }
  return(x)
}
```

```{r constants}
# Most constants have been placed in the file constants.R to unify the work across reporting and applications.

# Additional constants that are unique to this reporting engine can be added here.
id.name <- "id"
age.name <- "Age"
gender.name <- "Gender"
income.name <- "Income"
region.name <- "Region"
persona.name <- "Persona"

product.name <- "Product"
awareness.name <- "Awareness"
consideration.name <- "Consideration"
consumption.name <- "Consumption"
satisfaction.name <- "Satisfaction"
advocacy.name <- "Advocacy"

bp.pattern <- "BP_"

age.group.name <- "Age_Group"
income.group.name <- "Income_Group"
```

```{r read_data, include=FALSE, eval=TRUE}
data = fread(input = "xxx/mobile phone survey data.csv", verbose = F)
```

```{r define groups}
#define age group
data[18 <= Age & Age < 35, Age_Group := "[18,35)"]
data[35 <= Age & Age < 50, Age_Group := "[35,50)"]
data[50 <= Age & Age < 65, Age_Group := "[50,65)"]
data[65 <= Age, Age_Group := "[65,+)"]
data$Age_Group = as.factor(data$Age_Group)
#define income group
data[Income < 50000, Income_Group := "(-, 50000)"]
data[Income >= 50000 & Income < 75000, Income_Group := "[50000, 75000)"]
data[Income >= 75000 & Income < 100000, Income_Group := "[75000, 100000)"]
data[Income >= 100000 & Income < 150000, Income_Group := "[100000, 150000)"]
data[Income >= 150000, Income_Group := "[150000, +)"]
data$Income_Group = as.factor(data$Income_Group)
#turn other respondent variable into factor
data$id = as.factor(data$id)
data$Gender = as.factor(data$Gender)
data$Region = as.factor(data$Region)
data$Persona = as.factor(data$Persona)
data$Product = as.factor(data$Product)
```



```{r define variables}
data[, eval(satisfaction.name) := get(satisfaction.name) / 10]

unique.age.groups <- data[, sort(unique(get(age.group.name)))]
unique.genders <- data[, sort(unique(get(gender.name)))]
unique.income.groups <- data[, sort(unique(get(income.group.name)))]
unique.regions <- data[, sort(unique(get(region.name)))]
unique.personas <- data[, sort(unique(get(persona.name)))]

unique.products <- data[, unique(get(product.name))]

respondent.variables <- c(age.group.name, gender.name, income.group.name, region.name, persona.name)
states.of.engagement <- c(awareness.name, consideration.name, consumption.name, satisfaction.name, advocacy.name)
bp.traits <- names(data)[grep(pattern = bp.pattern, x = names(data))]
```


Introduction
=====================================  
We are analyzing data from the marketing survey of a telecommunication company. 

The survey was given to `r data[, length(unique(id))]` respondents and covered `r data[, length(unique(Product))]` separate products.

Click on the tabs to see different reports.

Respondent Variables
===================================


Row {data-height=500}
-------------------------------------

```{r q1_input}
inputPanel(
  selectInput(inputId="respondent_variable", label = "Select Variable:", choices = respondent.variables, selected = respondent.variables[1]),
  checkboxInput(inputId = "respondent_show_percentages", label = "Show Percentages", value = TRUE)
)
#input <- list(respondent_variable = respondent.variables[1], respondent_show_percentages = TRUE)
#print(input)
```

Row {data-height=500}
-------------------------------------

```{r q1_output}
renderPlot({
  tab <- percentage.table(x = data[get(product.name) == get(product.name)[1], get(input$respondent_variable)])
  barplot(height = tab, space=0.01, las = 1, main = input$respondent_variable, ylab = "Percentage", xlab = input$respondent_variable, ylim = c(0, 1.2*max(tab, na.rm = TRUE)), col = "dodgerblue")
  
  if(input$respondent_show_percentages == TRUE){
    space_val = 0
    text(x = -0.4 + 1:length(tab) * (1+space_val), y = tab, labels = sprintf("%.1f%%", tab), pos = 3)
  }
})
```

Segmented Outcomes
=====================================  


Row {data-height=500}
-------------------------------------

```{r q2_input}
inputPanel(
  selectInput(inputId = "product_info_engagement_state", label = "Select State of Engagement:", choices = states.of.engagement, selected = states.of.engagement[1]),
  
  #select age
  selectInput(inputId = "product_info_age", label = "Select Age:", choices = unique.age.groups, selected = unique.age.groups,multiple = TRUE),
  #select gender
  selectInput(inputId = "product_info_gender", label = "Select Gender:", choices = unique.genders, selected = unique.genders, multiple = TRUE),
  #select Income
  selectInput(inputId = "product_info_income", label = "Select Income:", choices = unique.income.groups, selected = unique.income.groups, multiple = TRUE),
  #select region
  selectInput(inputId = "product_info_region", label = "Select Region:", choices = unique.regions, selected = unique.regions, multiple = TRUE),
  #select persona
  selectInput(inputId = "product_info_persona", label = "Select Persona:", choices = unique.personas, selected = unique.personas, multiple = TRUE),
 
   checkboxInput(inputId = "product_info_decreasing", label = "Sorted", value=TRUE),
  checkboxInput(inputId = "product_info_show_percentages", label = "Show Percentages", value = TRUE),
  
sliderInput(inputId = "product_info_min_threshold", label = "Show Products Above", min = 0, max = 100, value = 20, step = 5),
  #select number of products
sliderInput(inputId = "product_info_num_product", label = "Number of Products", min = 0, max = 20, value = 10, step = 1),
  
sliderInput(inputId = "product_info_names_magnification", label = "Magnify Product Names", min = 0.4, max = 1.4, value = 1, step = 0.1)
)
# input <- list(product_info_engagement_state = states.of.engagement[1], product_info_decreasing = TRUE, product_info_show_percentages = TRUE, product_info_min_threshold = 20, product_info_names_magnification = 1)
```

Row {data-height=500}
-------------------------------------

```{r q2_output}
renderPlot({
  
  subdat <- data[get(age.group.name) %in% input$product_info_age & get(gender.name) %in% input$product_info_gender & get(income.group.name) %in% input$product_info_income & get(region.name) %in% input$product_info_region & get(persona.name) %in% input$product_info_persona]
  
  rates <- subdat[, .(Mean = 100*mean(get(input$product_info_engagement_state), na.rm=TRUE)/max(get(input$product_info_engagement_state), na.rm = TRUE)), by = product.name]

  if(input$product_info_decreasing == TRUE){
    setorderv(x = rates, cols = "Mean", order = -1)
  }  
  barplot(height = rates[Mean > input$product_info_min_threshold,  Mean], names.arg = rates[Mean > input$product_info_min_threshold, get(product.name)], space=0.01, las = 1, main = input$product_info_engagement_state, ylab = sprintf("Rate of %s", input$product_info_engagement_state), cex.names = input$product_info_names_magnification, ylim = c(-100, 120), xlim = c(0,input$product_info_num_product), xaxt = "n", axes = F, col = "dodgerblue")
  axis(side = 2, at = 20*(0:5), las = 2)
  
  text(x = -0.5 + 1.02*1:rates[Mean > input$product_info_min_threshold, .N], y = -15, labels = rates[Mean > input$product_info_min_threshold, get(product.name)], srt = 45, cex = input$product_info_names_magnification, pos = 2)
  
  if(input$product_info_show_percentages == TRUE){
    space_val = 0
    text(x = -0.4 + 1:rates[Mean > input$product_info_min_threshold, .N] * (1+space_val), y = rates[Mean > input$product_info_min_threshold, Mean], labels = sprintf("%.1f%%", rates[Mean > input$product_info_min_threshold, Mean]), pos = 3)

  }
})
```


Overall Brand Perceptions
=====================================  

Row {data-height=500}
-------------------------------------

```{r q3_input}
inputPanel(
   #select age
  selectInput(inputId = "bp_age", label = "Select Age:", choices = unique.age.groups, selected = unique.age.groups, multiple = TRUE),
  #select gender
  selectInput(inputId = "bp_gender", label = "Select Gender:", choices = unique.genders, selected = unique.genders, multiple = TRUE),
  #select Income
  selectInput(inputId = "bp_income", label = "Select Income:", choices = unique.income.groups, selected = unique.income.groups, multiple = TRUE),
  #select region
  selectInput(inputId = "bp_region", label = "Select Region:", choices = unique.regions, selected = unique.regions, multiple = TRUE),
  #select persona
  selectInput(inputId = "bp_persona", label = "Select Persona:", choices = unique.personas, selected = unique.personas, multiple = TRUE),

  checkboxInput(inputId = "bp_decreasing", label = "Sorted", value=TRUE),
    #select number of products
sliderInput(inputId = "bp_num_product", label = "Number of Products", min = 0, max = 20, value = 10, step = 1),

sliderInput(inputId = "bp_min_threshold", label = "Show Products Above", min = 0, max = 10, value = 0, step = 1),
  checkboxInput(inputId = "bp_show_percentages", label = "Show Percentages", value = TRUE),

sliderInput(inputId = "bp_names_magnification", label = "Magnify Product Names", min = 0.4, max = 1.4, value = 1, step = 0.1)
)

# input <- list(bp_product = unique.products[1], bp_trait = bp.traits[1], bp_show_percentages = TRUE)
```

Row {data-height=500}
-------------------------------------

```{r q3_output}
renderPlot({
  
  subdat <- data[get(age.group.name) %in% input$bp_age & get(gender.name) %in% input$bp_gender & get(income.group.name) %in% input$bp_income & get(region.name) %in% input$bp_region & get(persona.name) %in% input$bp_persona]
  
  #compute average by products
avg = subdat[,.(BP_User_Friendly_0_10 = mean(BP_User_Friendly_0_10, na.rm = TRUE),
BP_Fast_0_10 = mean(BP_Fast_0_10, na.rm = TRUE),
BP_Battery_Life_0_10 = mean(BP_Battery_Life_0_10, na.rm = TRUE),
BP_Camera_0_10 = mean(BP_Camera_0_10, na.rm = TRUE),
BP_Sleek_0_10 = mean(BP_Sleek_0_10, na.rm = TRUE),
BP_Stylish_0_10 = mean(BP_Stylish_0_10, na.rm = TRUE),
BP_Status_Symbol_0_10 = mean(BP_Status_Symbol_0_10, na.rm = TRUE),
BP_Good_Screen_Size_0_10 = mean(BP_Good_Screen_Size_0_10, na.rm = TRUE),
BP_Boring_0_10 = mean(BP_Boring_0_10, na.rm = TRUE),
BP_Bulky_0_10 = mean(BP_Bulky_0_10, na.rm = TRUE),
BP_Fragile_0_10 = mean(BP_Fragile_0_10, na.rm = TRUE),
BP_Expensive_0_10 = mean(BP_Expensive_0_10, na.rm = TRUE)), by = "Product"]
#avg

#invert nagative perception
#BP_Boring_0_10
#BP_Bulky_0_10
#BP_Fragile_0_10
#BP_Expensive_0_10
avg[,.(BP_User_Friendly_0_10,BP_Fast_0_10,BP_Battery_Life_0_10,BP_Camera_0_10,BP_Sleek_0_10,BP_Stylish_0_10,BP_Status_Symbol_0_10,BP_Good_Screen_Size_0_10,BP_Boring_0_10 = 10-BP_Boring_0_10, BP_Bulky_0_10 = 10-BP_Bulky_0_10,BP_Fragile_0_10 = 10-BP_Fragile_0_10,BP_Expensive_0_10 = 10-BP_Expensive_0_10), by ="Product"]
  
  rates <- avg[, .(Mean = mean(get(bp.traits))), by = "Product"]

  if(input$bp_decreasing == TRUE){
    setorderv(x = rates, cols = "Mean", order = -1)
  }  
  barplot(height = rates[Mean > input$bp_min_threshold,  Mean], names.arg = rates[Mean >  input$bp_min_threshold, get(product.name)], space=0.01, las = 1, main = "Brand Perception", ylab = sprintf("Rate of %s", "Perception"), cex.names = input$bp_names_magnification, ylim = c(-5, 10), xlim = c(0,input$bp_num_product), xaxt = "n", axes = F, col = "dodgerblue")
  axis(side = 2, at = 20*(0:5), las = 2)
  
  text(x = -0.5 + 1.02*1:rates[Mean > input$bp_min_threshold, .N], y = -1, labels = rates[Mean > input$bp_min_threshold, get(product.name)], srt = 45, cex = input$bp_names_magnification, pos = 2)
  
  if(input$bp_show_percentages == TRUE){
    space_val = 0
    text(x = -0.4 + 1:rates[Mean > input$bp_min_threshold, .N] * (1+space_val), y = rates[Mean > input$bp_min_threshold, Mean], labels = sprintf("%.1f", rates[Mean > input$bp_min_threshold, Mean]), pos = 3)
  }
})
```

Gaps in Outcomes
=====================================  

Row {data-height=500}
-------------------------------------

```{r q4_input}
inputPanel(
  selectInput(inputId = "engagement_state1", label = "Select First Engagement:", choices = states.of.engagement, selected = states.of.engagement[1]),
  selectInput(inputId = "engagement_state2", label = "Select Second Engagement:", choices = states.of.engagement, selected = states.of.engagement[2]),
 
   checkboxInput(inputId = "q4_decreasing", label = "Sorted", value=TRUE),
  checkboxInput(inputId = "q4_show_percentages", label = "Show Percentages", value = TRUE),
  
sliderInput(inputId = "q4_min_threshold", label = "Show Products Above", min = 0, max = 100, value = 20, step = 1),
  #select number of products
sliderInput(inputId = "q4_num_product", label = "Number of Products", min = 0, max = 20, value = 10, step = 1),
  
sliderInput(inputId = "q4_names_magnification", label = "Magnify Product Names", min = 0.4, max = 1.4, value = 1, step = 0.1),
sliderInput(inputId = "q4_percent", label = "Number of Digits", min = 0, max = 10, value = 1, step = 1)
)
```

Row {data-height=500}
-------------------------------------

```{r q4_output}
renderPlot({
  rates <- data[, .(Mean = abs(100*mean(get(input$engagement_state1), na.rm=TRUE) - 100*mean(get(input$engagement_state2), na.rm=TRUE))), by = product.name]

  if(input$q4_decreasing == TRUE){
    setorderv(x = rates, cols = "Mean", order = -1)
  }  
  barplot(height = rates[Mean > input$q4_min_threshold,  Mean], names.arg = rates[Mean > input$q4_min_threshold, get(product.name)], space=0.01, las = 1, main = "Difference", ylab = sprintf("Rate of %s", "Difference"), cex.names = input$q4_names_magnification, ylim = c(-100, 100), xlim = c(0,input$q4_num_product), xaxt = "n", axes = F, col = "dodgerblue")
  axis(side = 2, at = 20*(0:5), las = 2)
  
  text(x = -0.5 + 1.02*1:rates[Mean > input$q4_min_threshold, .N], y = -15, labels = rates[Mean > input$q4_min_threshold, get(product.name)], srt = 45, cex = input$q4_names_magnification, pos = 2)
  
  if(input$q4_show_percentages == TRUE){
    space_val = 0
    text(x = -0.4 + 1:rates[Mean > input$q4_min_threshold, .N] * (1+space_val), y = rates[Mean > input$q4_min_threshold, Mean], labels = sprintf("%.*f%%",input$q4_percent, rates[Mean > input$q4_min_threshold, Mean]), pos = 3)
  }
  
})

```

Aggregated Engagement
=====================================  

Row {data-height=500}
-------------------------------------


```{r q5_input}
inputPanel(
  selectInput(inputId="em_state", label = "State of Engagement:", choices = states.of.engagement, selected = states.of.engagement[1]),
  selectInput(inputId="em_product", label = "Brand", choices = unique.products, selected = unique.products[1], multiple = FALSE),
  selectInput(inputId="em_inputs", label = "Choose Inputs:", choices = c(age.group.name, gender.name, region.name, income.group.name, persona.name, bp.traits), 
              selected = c(age.group.name, gender.name, region.name, income.group.name), multiple = TRUE),
  
  selectInput(inputId="em_age_group", label = "Age", choices = unique.age.groups, selected = unique.age.groups, multiple = TRUE),
  selectInput(inputId = "em_gender", label = "Gender", choices = unique.genders, selected = unique.genders, multiple = TRUE),
  selectInput(inputId = "em_income_group", label = "Income", choices = unique.income.groups, selected = unique.income.groups, multiple = TRUE),
  selectInput(inputId = "em_region", label = "Region", choices = unique.regions, selected = unique.regions, multiple = TRUE),
  selectInput(inputId = "em_persona", label = "Persona", choices = unique.personas, selected = unique.personas, multiple = TRUE),
  checkboxInput(inputId = "q5_agg_eng", label = "Aggregated Engagement", value=FALSE)
)
```

Row {data-height=500}
-------------------------------------

```{r q5_output}
renderDataTable({
  
  subdat <- data[get(product.name) %in% input$em_product & get(age.group.name) %in% input$em_age_group & get(gender.name) %in% input$em_gender & get(income.group.name) %in% input$em_income_group & get(region.name) %in% input$em_region & get(persona.name) %in% input$em_persona]
  
  
  if(input$em_state == satisfaction.name){
    model.type <- "linear"
  }
  if(input$em_state != satisfaction.name){
    model.type <- "logistic"
  }
  
  
  if(input$q5_agg_eng == TRUE){
     #satisfaction
#Buzzdial 
Buzz_Satf = data[Product != input$em_product, .(Engagement = mean(get(input$em_state), na.rm = TRUE)), by = "id"]
#merge table
bs = merge(Buzz_Satf, data[, .SD, .SDcols = c("id","Age_Group", "Gender", "Income_Group", "Region", "Persona")], by = "id")
bss = merge(bs, data[Product == input$em_product, .SD, .SDcols = c("id", input$em_state)], by = "id")
  
    res <- fit.model(dt = bss, outcome.name = input$em_state, input.names = c(input$em_inputs, bss$Engagement), model.type = model.type)
  }
  if(input$q5_agg_eng != TRUE){
    
    res <- fit.model(dt = subdat, outcome.name = input$em_state, input.names = input$em_inputs, model.type = model.type)
  }
  
  datatable(data = res)
})

```

